Formula 1 2022 Regulation Changes

### 2024-04-04 paper/paper.qmd
updated intro and abstract

---
title: "Formula 1 2022 Regulation Changes"
subtitle: "How did the 2022 F1 Regulations change the sport for better and for worse"
author: 
  - Michael Fang
thanks: "Code and data are available at: https://github.com/fanger2791/F1_Regulations."
date: today
date-format: long
abstract: "As Formula 1's new era of hybrid cars develops, a fresh range of rules and regulations have been put in place for the teams to follow attempting to create a closer, more competitive championship. This paper will investigate the impact of the 2022 Formula 1 regulations, designed to intensify the competitive landscape and elevate the racing experience through technical and fiscal adjustments. Leveraging an in-depth examination of lap times and overtaking dynamics, the analysis zeroes in on the performance trajectories of the sport’s leading contenders: Max Verstappen, Lewis Hamilton, and Charles Leclerc across varied circuit types from 2021 to 2022. The investigation aims to reveal whether these regulatory modifications have indeed leveled the playing field, creating tighter competition and mitigating the performance differences between teams or have largened the gap even more. This research not only examines the immediate effects of the 2022 changes but also provides crucial insights into the balance between innovation and competition in Formula 1, thereby contributing to the ongoing dialogue on how to shape the future of this high-stakes sport."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

Despite these debates, preliminary findings suggest that the 2022 regulations have had a profound impact on Formula 1. Races have generally become more competitive, with a wider array of teams and drivers finding themselves in contention for podium finishes. The budget cap has also initiated a more strategic allocation of resources among teams, potentially leveling the competitive field over the longer term. The paper's estimand is that the 2022 Formula 1 regulations led to a significant increase in lap time in comparison to the previous time among the top drivers across different types of circuits but also increased the number of successful overtakes during races. This estimand aims to quantify the impact of the 2022 Formula 1 regulatory changes, providing a clear basis for evaluating their success in enhancing the sport's competitive balance and the quality of racing.

>>>>

---
title: "Formula 1 2022 Regulation Changes"
subtitle: "How did the 2022 F1 Regulations change the sport for better and for worse"
author: 
  - Michael Fang
thanks: "Code and data are available at: https://github.com/fanger2791/F1_Regulations."
date: today
date-format: long
abstract: "As Formula 1's new era of hybrid cars develops, a fresh range of rules and regulations have been put in place for the teams to follow attempting to create a closer, more competitive championship. This paper will investigate the impact of the 2022 Formula 1 regulations, designed to intensify the competitive landscape and elevate the racing experience through technical and fiscal adjustments. It examines lap times and overtaking dynamics, while the analysis zeroes in on the performance trajectories of the sport’s leading contenders: Max Verstappen, Lewis Hamilton, and Charles Leclerc across varied circuit types from 2021 to 2022. It focuses on whether these regulatory modifications have indeed leveled the playing field, creating tighter competition and mitigating the performance differences between teams or have increased the gap even more. This research not only examines the immediate effects of the 2022 changes but also considers the balance between innovation and competition in Formula 1, thereby contributing to the ongoing dialogue on how to shape the future of this high-stakes sport."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

Despite these debates, preliminary findings suggest that the 2022 regulations have had a profound impact on Formula 1. Races have generally become more competitive, with a wider array of teams and drivers finding themselves in contention for podium finishes. The budget cap has also initiated a more strategic allocation of resources among teams, potentially leveling the competitive field over the longer term. The paper's estimand is whether the 2022 Formula 1 regulations led to a significant increase in lap time in comparison to the previous time among the top drivers across different types of circuits but also increased the number of successful overtakes during races. We aim to quantify the impact of the 2022 Formula 1 regulatory changes, providing a clear basis for evaluating their success in enhancing the sport's competitive balance and the quality of racing.
